Data Migration under a Changing Schema

### 2023-07-07 2022Migration/articleMigrationFACS.tex
Dealing with violations update: added warnings

   Two extra relations are used: one to track the violations that occur in the original data (\ref{violRelation}), and one to track the violations that have been fixed (\ref{fixedRelation}) which prevents them from recurring.
   \begin{align}
   &\text{\tt RELATION viols\_UNI[Course*Course]}\label{violRelation}\\
   &\text{\tt RELATION fixed\_UNI[Course*Course]}\label{fixedRelation}\\
   &\text{\tt ENFORCE viols\_UNI >: old.isPartOf\textasciitilde;old.isPartOf - I}\label{fill viols}\\
   &\text{\tt ENFORCE fixed\_UNI >: viols\_UNI - (old.isPartOf\textasciitilde;old.isPartOf - I)}\label{fill fixed}\\
   &\begin{aligned}
   \text{\tt RULE isPartOf\_UNI: old.isPartOf\textasciitilde;old.isPartOf}\\
   \quad\text{\tt |- I \textbackslash/ (viols\_UNI - fixed\_UNI)}
   \end{aligned}\label{rule uni}
   \end{align}

@@

>>>>

   Two extra relations are used: one to track the violations that occur in the original data (\ref{violRelation}), and one to track the violations that have been fixed (\ref{fixedRelation}) which prevents them from recurring.
   \begin{align}
   &\text{\tt RELATION viols\_UNI[Course*Course]}\label{violRelation}\\
   &\text{\tt RELATION fixed\_UNI[Course*Course]}\label{fixedRelation}\\
   &\text{\tt ENFORCE viols\_UNI >: old.isPartOf\textasciitilde;old.isPartOf - I}\label{fill viols}\\
   &\text{\tt ENFORCE fixed\_UNI >: viols\_UNI - (old.isPartOf\textasciitilde;old.isPartOf - I)}\label{fill fixed}\\
   &\begin{aligned}
   \text{\tt RULE isPartOf\_UNI: new.isPartOf\textasciitilde;new.isPartOf}\\
   \quad\text{\tt |- I \textbackslash/ (viols\_UNI - fixed\_UNI)}
   \end{aligned}\label{rule uni}
   \end{align}

@@

   We also wish to alert users with the role `migration helper' to violations that need to be fixed.
   For the original \verb=UNI= requirement, this means specifying:

   \begin{align}
   \begin{aligned}
   \text{\tt RULE isPartOf\_UNI\_warn: new.isPartOf\textasciitilde;new.isPartOf |- I}\\
   \quad\text{\tt RULE MigrationHelper}
   \end{aligned}\label{warnings}
   \end{align}

   Despite the syntax, Line~{\ref{warnings}} is not a rule of the generated information system:
   By assigning a role, the responsibility of maintaining the rule no longer lies with the information system.
   Instead, users with the migration helper role can see the violations and act on it as they see fit.
